Working with Code environments in texor

### 2023-09-28 supplement/code-env/code-example.tex
Fixed #19

S series code environement is defined in Rjournal.sty file. Most of these are
extensions of verbatim environment and are represented as vanilla verbatim in HTML.

@@

\subsection{Example series}
Example series of code environment is defined in Rjournal.sty file. Examples are
extensions of verbatim environment and are represented as vanilla verbatim in HTML.

>>>>

S series code environement is defined in Rjournal.sty file. Most of these are
extensions of verbatim environment and retain the original formatting of the content
in HTML.

@@

\subsection{Example series}
Example series of code environment is defined in Rjournal.sty file. Examples are
extensions of verbatim environment and retain the original formatting of the content
in HTML.
